Bricking up and overgrowing backdoors in Intrusion Detection Systems

### 2019-09-06 ex2/paper/pruning_example.tex
Finish pruning_example.tex

\documentclass[border=10pt]{standalone}
\usepackage{forest}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{calc}

\forestset{
  default preamble={
    before typesetting nodes={
      !root.replace by={[, coordinate, append, name=veryTop]}
    },
    where n children>=1{
      diamond, aspect=2,
    }{},
    where level=0{}{
      if n=1{
        edge label={node[pos=.2, above] {Y}},
      }{
        edge label={node[pos=.2, above] {N}},
      }
    },
    for tree={
      edge+={thick, -Latex},
      math content,
      s sep'+=2cm,
%      l sep'=0cm,
      draw,
      thick,
      edge path'={ (!u) -| (.parent)},
    }
  }
}

\begin{document}
\begin{forest} 
    [x_2 \leq 3.1, name=top
        [x_1 \leq -2, name=l2l
            [1, name=leftmost] 
            [0] 
        ]   
        [x_3 \leq 105
            [x_1 \leq 1.6, name=l2m
              [0, name=bottom] 
              [1] 
            ]   
            [0, name=rightmost] 
        ]   
    ]
        {
        \draw[red] let \p{veryTop.north}=(veryTop.north), \p{top.south}=(top.south), \p{leftmost.west}=(leftmost.west), \p{rightmost.east}=(rightmost.east) in (\x{leftmost.west},\y{top.south}) rectangle (\x{rightmost.east},\y{veryTop.north});
        \draw[red] let \p{lx}=(leftmost.west), \p{ly}=(l2l.south), \p{rx}=(rightmost.east), \p{ry}=(top.south) in (\x{lx},\y{ly}) rectangle (\x{rx},\y{ry});
        }
        \draw[red] let \p{lx}=(leftmost.west), \p{ly}=(l2l.south), \p{rx}=(rightmost.east), \p{ry}=(top.south) in (\x{lx},\y{ly}) rectangle (\x{rx},\y{ry});
        }
\end{forest}
\end{document}

>>>>

\documentclass[border=10pt]{standalone}
\usepackage[dvipsnames]{xcolor}
\usepackage{forest}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{calc}
\usetikzlibrary{patterns}
\usepackage{adjustbox}

%\newcommand{\goodNodeStyle}{pattern=north west lines, pattern color=gray}
\newcommand{\goodNodeStyle}{fill opacity={0.2}, fill=green}

\tikzset{
  my box/.style={color=#1},
%  align at top/.style={baseline=(current bounding box.north)},
}

\forestset{ 
  my depth label/.style={
    label={[my box=Fuchsia]right:#1},
  },
  my usages label/.style={
    label={[my box=MidnightBlue]left:#1},
  },
  default preamble={
    before typesetting nodes={
      !root.replace by={[, coordinate, append, name=veryTop]}
    },
    where n children>=1{
      diamond, aspect=2,
    }{},
    where level=0{}{
      if n=1{
        edge label={node[pos=.2, above] {Y}},
      }{
        edge label={node[pos=.2, above] {N}},
      }
    },
    for tree={
      edge+={thick, -Latex},
      math content,
      s sep+=2cm,
%      l sep=0cm,
      draw,
      thick,
      edge path'={ (!u) -| (.parent)},
    }
  }
}

\newcommand{\topspace}{0.5cm}

\begin{document}

\begin{adjustbox}{valign=t}
\begin{forest}      
    [x_2 \leq 3.1, name=top
        [x_1 \leq -2, name=l2l
            [1, tier=3, my usages label=10, my depth label=3] 
            [0, tier=3, my usages label=3, my depth label=3, \goodNodeStyle]
        ]   
        [x_3 \leq 105
            [x_1 \leq 1.6, tier=3
              [0, my usages label=0, my depth label=4, \goodNodeStyle] 
              [1, my usages label=1, my depth label=4] 
            ]   
            [0, edge+= dashed, my usages label=0, my depth label=3, tier=3, \goodNodeStyle] 
        ]   
    ]
    \node[above=\topspace ,align=center,anchor=center] {\textsf{Step 0}};
{}
\end{forest}
\end{adjustbox}

\begin{adjustbox}{valign=t}
\begin{forest}    
    [x_2 \leq 3.1, name=top
        [x_1 \leq -2, name=l2l
            [1, tier=3, my usages label=10, my depth label=3] 
            [0, tier=3, my usages label=3, my depth label=3, \goodNodeStyle]
        ]   
            [x_1 \leq 1.6,
              [0, edge+=dashed, my usages label=0, my depth label=4, \goodNodeStyle] 
              [1, my usages label=1, my depth label=4] 
            ]   
        ]   
    ]
    \node[above=\topspace ,align=center,anchor=center] {\textsf{Step 1}};
{}
\end{forest}
\end{adjustbox}

\begin{adjustbox}{valign=t}
\begin{forest}    
    [x_2 \leq 3.1, name=top
        [x_1 \leq -2, name=l2l
            [1, tier=3, my usages label=10, my depth label=3] 
            [0, edge+=dashed, tier=3, my usages label=3, my depth label=3, \goodNodeStyle]
        ]   
              [1, my usages label=1, my depth label=4] 
        ]   
    ]
    \node[above=\topspace ,align=center,anchor=center] {\textsf{Step 2}};
{}
\end{forest}
\end{adjustbox}

\begin{adjustbox}{valign=t}
\begin{forest}    
    [x_2 \leq 3.1, name=top
            [1, my usages label=10, my depth label=3] 
              [1, my usages label=1, my depth label=4] 
        ]   
    ]
    \node[above=\topspace ,align=center,anchor=center] {\textsf{Step 3}};
{}
\end{forest}
\end{adjustbox}

\end{document}
